---
title: "Untitled"
output: html_document
date: "2025-08-29"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


load library
```{r message=FALSE, warning=FALSE}
library(dplyr)
library(here)
library(ggplot2)
library(stringr)
library(R.utils)
library(rlang)
library(tidyr)
library(jtools)
library(ggpubr)
```

load scripts
```{r}
source("word-catalog.R")
source("items-and-labels.R")
source("data-preprocessing.R")
source("visualization.R")
source("utils.R")
source("simulation.R")
```

## Load and Preprocess data
```{r}
# df_raw = read.csv("data/results.csv")
# df = preprocessData(df_raw, all_items)

df = simulate_data()
```

## Inclusion Criteria 

1. Debrief consent = Y
2. Demographic Criteria 
 2.1 AGE >= 18
 2.2 SEX = M
 2.3 GER = Muttersprache
3. Suspicion
  3.1. OPENFEEDBACK auswerten
  3.2. SUS & SUSTEXT auswerten
4. WFCT comprehension check
  => More than 50% are real words...

### 1. Debrief Consent
```{r}
df = df %>% 
  filter(DEBRIEFCONSENT == "Y")
count(df)$n
```

### 2. Demographic criteria
```{r}
df = df %>% 
  filter(AGE >= 18) %>% 
  filter(SEX == "AO01") %>% 
  filter(GER == "AO05")
count(df)$n
```

### 3. Suspicion

TODO

### 4. WFCT comprehension

```{r}
df = df %>% 
  filter(validWordCompletionScore >= 0.5)
count(df)$n
```

## Descriptive Analysis

### Age
```{r}
df %>%
  summarise(
    mean_age = round(mean(AGE, na.rm = TRUE), 2),
    sd_age = round(sd(AGE, na.rm = TRUE), 2),
  )
```

### Manipulation Check

```{r}
## [GKFEEDBACK] Welche R체ckmeldung haben Sie im Verlauf der Studie zu Ihrem Wissen in geschlechtsspezifischen Themen erhalten?
## Scale 1 to 10

plotHist("GKFEEDBACK",c(1,10),  "threatCondition") +
  labs(
    # title = "Welche R체ckmeldung haben SIe erhalten?",
    x = NULL,
    y = "Anzahl",
    fill = "Bedingung"
  )

```

```{r}
## [GKSELF] Wie w체rden Sie Ihr Wissen in geschlechtsspezifischen Themen einsch채tzen?
plotHist("GKSELF", c(1,10)) + 
  labs(
    x = NULL,
    y = "Anzahl"
  ) 
```



### Educational and OCcupational Degree

```{r}
plotBarHorizontal("EDU_label") + 
  labs(
    x = NULL,
    y = "Anzahl"
  ) 

plotBarHorizontal("OCC_label") + 
  labs(
    x = NULL,
    y = "Anzahl"
  ) 
```


### Valid Word Completions

```{r}
df %>%
  summarise(
    mean_valid = round(mean(validWordCompletionScore, na.rm = TRUE), 2),
    sd_valid = round(sd(validWordCompletionScore, na.rm = TRUE), 2),
  )
```

```{r}
plotBox("validWordCompletionScore")
```

### Motivation for Masculine Behaviour

```{r}
plotHist("mmb_autonomous_score", c(1,7))
plotHist("mmb_pressured_score", c(1,7))

p = plotBox(c("mmb_autonomous_score", "mmb_pressured_score"))
ggpar(p, ylim = c(1, 7))
```

### Visualization Hypothesis 1a & 1b

Aggessive and axious word completions by threat condition
```{r}
plotBox(c("aggressiveWordCompletionScore", "anxiousWordCompletionScore"), "threatCondition")
```

```{r}
df %>%
  group_by(threatCondition) %>%
  summarise(
    mean_aggressive = round(mean(aggressiveWordCompletionScore, na.rm = TRUE), 2),
    sd_aggressive = round(sd(aggressiveWordCompletionScore, na.rm = TRUE), 2),
  )

df %>%
  group_by(threatCondition) %>%
  summarise(
    mean_anxious = round(mean(anxiousWordCompletionScore, na.rm = TRUE), 2),
    sd_anxious = round(sd(anxiousWordCompletionScore, na.rm = TRUE), 2)
  )
```

```{r}
df %>%
  summarise(
    mean_autonomous = round(mean(mmb_autonomous_score, na.rm = TRUE), 2),
    sd_autonomous = round(sd(mmb_autonomous_score, na.rm = TRUE), 2),
  )

df %>%
  summarise(
    mean_pressured = round(mean(mmb_pressured_score, na.rm = TRUE), 2),
    sd_pressured = round(sd(mmb_pressured_score, na.rm = TRUE), 2)
  )
```

### Visualization Hypothesis 2a & 2b

2a: Moderation autonomous motivation for masculine behavior on aggressive word completions
```{r}
plotLine("mmb_autonomous_score", "anxiousWordCompletionScoreTransformed", condition = "threatCondition", df = df)
```

2b: Moderation pressured motivation for masculine behavior on aggressive word completions
```{r}
plotLine("mmb_pressured_score", "aggressiveWordCompletionScoreTransformed", condition = "threatCondition", df = df)
```





