---
title: "Untitled"
author: "Linus Widmer"
date: "2025-07-21"
output: html_document
---

load library
```{r}
library(dplyr)
library(here)
library(ggplot2)
library(stringr)
library(R.utils)
library(rlang)
library(tidyr)
library(jtools)
library(ggpubr)
```

load scripts
```{r}
source("word-catalog.R")
source("items-and-labels.R")
source("data-preprocessing.R")
source("visualization.R")
source("utils.R")
```

## Load and Preprocess data
```{r}
df_raw = read.csv("data/results-pre-test.csv")
df = preprocessData(df_raw, all_items)
```

## Exclusion Criteria 

1. Debrief consent = Y
2. Study inclusion Criteria 
 2.1 AGE >= 18
 2.2 SEX = M
 2.3 GER = Muttersprache
3. Manipulation Control
  3.1. GKFEEDBACK = depending on ThreatCondition
  3.2. OPENFEEDBACK auswerten
  3.3. SUS & SUSTEXT auswerten
4. WFCT comprehension check
  => More than 50% are real words...

### Debrief Consent
```{r}
df = df %>% 
  filter(DEBRIEFCONSENT == "Y")
count(df)$n
```


Study inclusion criteria
```{r}
df = df %>% 
  filter(AGE >= 18) %>% 
  filter(SEX == "AO01") 
  # %>% filter(GER == "AO05") 
count(df)$n
```

Manipulation control
```{r}

plotBarHorizontal("GKFEEDBACK_label", "threatCondition") +
  labs(
    # title = "Welche Rückmeldung haben SIe erhalten?",
    x = NULL,
    y = "Anzahl",
    fill = "Bedingung"
  )

```

```{r}
table(df$GKFEEDBACK, df$threatCondition)
table(df$GKSELF)
```


## Descriptive Analysis

### Age
```{r}
df %>%
  summarise(
    mean_age = round(mean(AGE, na.rm = TRUE), 2),
    sd_age = round(sd(AGE, na.rm = TRUE), 2),
  )
```

## Educational and OCcupational Degree

```{r}
plotBarHorizontal("EDU_label") + 
  labs(
    x = NULL,
    y = "Anzahl"
  ) 

plotBarHorizontal("OCC_label") + 
  labs(
    x = NULL,
    y = "Anzahl"
  ) 

plotBarHorizontal("GKSELF_label") + 
  labs(
    x = NULL,
    y = "Anzahl"
  ) 
```

## Aggressive and Anxious Word Completions


```{r}
df %>%
  group_by(threatCondition) %>%
  summarise(
    mean_aggressive = round(mean(aggressiveWordCompletionScore, na.rm = TRUE), 2),
    sd_aggressive = round(sd(aggressiveWordCompletionScore, na.rm = TRUE), 2),
  )

df %>%
  group_by(threatCondition) %>%
  summarise(
    mean_anxious = round(mean(anxiousWordCompletionScore, na.rm = TRUE), 2),
    sd_anxious = round(sd(anxiousWordCompletionScore, na.rm = TRUE), 2)
  )
```

```{r}
plotBox(c("aggressiveWordCompletionScore", "anxiousWordCompletionScore"), "threatCondition")
```


## Motivation for Masculine Behaviour
```{r}

df$mmb_autonomous_score = rowMeans(
    df[MMB_autonomous_items],
    na.rm = TRUE
  )

df$mmb_pressured_score = rowMeans(
    df[MMB_pressured_items],
    na.rm = TRUE
  )
```


```{r}
plotHist("mmb_autonomous_score", c(1,7))
plotHist("mmb_pressured_score", c(1,7))

p = plotBox(c("mmb_autonomous_score", "mmb_pressured_score"))
ggpar(p, ylim = c(1, 7))
```


```{r}
df %>%
  summarise(
    mean_autonomous = round(mean(mmb_autonomous_score, na.rm = TRUE), 2),
    sd_autonomous = round(sd(mmb_autonomous_score, na.rm = TRUE), 2),
  )

df %>%
  summarise(
    mean_pressured = round(mean(mmb_pressured_score, na.rm = TRUE), 2),
    sd_pressured = round(sd(mmb_pressured_score, na.rm = TRUE), 2)
  )
```




